\chapter{Abstract} \label{ch:abstract}

\textbf{Purpose:} Accurate contouring is a critical aspect of safe and effective
treatment delivery in radiotherapy (RT). Current limitations in clinical
practice include large intra and inter-observer variances (IOV), as well as time
delays in both contour generation and correction. This study designed and
evaluated a 2D U-Net architecture with two primary aims: 1) Develop a pelvic
imaging quality assurance tool for use in RT, comparing model predictions with
expert contours. 2) Automate vacuum bag segmentation for canine RT.

\textbf{Method:} This study presents two independently trained models and
assesses the performance of common semantic segmentation loss functions in each
case. The original U-Net architecture developed by Ronneberger et al. was
expanded by integrating recent network modifications that indicated improved
performance in the literature. In addition to reporting dice similarity
coefficients (DSC), organ-specific tolerances (representative of expert IOV) are
utilised for bladder and rectum contouring to quantify Nikolov et al.'s surface
dice similarity coefficient (sDSC) - reported to have a stronger
correlation with contour correction times when compared to traditional metrics.
The pelvic imaging dataset consisted of 15 patients undergoing RT for prostate
cancer, and was split into training, validation, and testing subsets of 12, 2,
and 1, respectively. The canine imaging dataset included 26 patients selected
from varied RT treatment groups, split into subsets of 21, 3, and 2, respectively.

\textbf{Results:}\footnote{Notation: $\bar{x}(\sigma)$ corresponds to a
measurement with mean value $\bar{x}$ and standard deviation $\sigma$.} Three
contours were produced from pelvic CT: Patient contours were measured with DSC
$0.998(0.001)$, bladder contours with DSC $0.9(0.2)$ and sDSC $0.9(0.2)$, and
rectum contours with DSC $0.7(0.1)$ and sDSC $0.9(0.1)$. Vacuum bag contours
from canine CT were measured with DSC $0.952(0.001)$. Weighted DSC was the only
loss function that optimised for all organs considered in pelvic imaging -
due to a significant pixel-wise class imbalance between structures.

\textbf{Conclusion:} Patient contours did not deviate outside of tolerances and
are viable for use within the QA tool in their current form. Bladder and rectum
segmentation may improve with a broader dataset. Additionally, a 3D model may
provide axial context to improve segmentation on rectal regions containing gas.
In its current implementation, the surface dice similarity coefficient accepts
only binary input data; hence, gradients are not defined when used as a cost
function. Developing a soft surrogate may allow for the direct optimisation of
this metric. The canine imaging model was successfully deployed to clinic under
a prototype warning, where preliminary acceptance testing has shown a
performance improvement of approximately 30 minutes per patient. It is currently
being utilised on all new canine patients undergoing RT.
