\chapter{Acknowledgements}
\label{ch:acknowledgements}

The author wishes to acknowledge the following:

\textbf{Simon Biggs}

For his mentorship and support over the course of the project. Simon played a pivotal role
in shaping the author's philosophy of code development. In addition, he facilitated the
author's first professional connections with\todo{within?} the medical physics community.

\textbf{Dr. Yu Sun}

For his encouragement and guidance throughout the Master of Medical Physics degree. Yu Sun has also been key in expanding the author's professional network - increasing the exposure of this project.

\textbf{Matthew Sobolewski}

Matthew provided valuable feedback and guidance on both the presentation and the research report. The author wishes to thank Matthew for supporting the first student research project at Riverina Cancer Care Centre.

\textbf{The team at Riverina Cancer Care Centre}\todo{teams at \ldots and Small Animal Specialist Hospital}

In particular: Jacob McAloney, Nick Menzies, and
Simon Biggs, for providing accommodation in their own homes over the course of
the project. This allowed the author to gain formative clinical experience. Additionally, this project would not have been possible without the data provided by Riverina Cancer Care Centre (RCCC) and the Small Animal Specialist Hospital (SASH). The medical physics team at RCCC also provided valuable feedback on the presentation.


\textbf{Dr. Annette Haworth \& Dr. Sianne Oktaria}

For going above and beyond to ensure March-\todo{--}June 2020 research students were able to complete their projects on time and remotely during the COVID-19 pandemic.

\textbf{Dr. Robert Finnegan}

For providing detailed feedback on the presentation.

\textbf{The team at DeepMind}

For making public their surface-distance-based performance metrics.

\url{https://github.com/deepmind/surface-distance}
